Thermodynamic fragments in magic state theories

### 2021-02-14 magic_paper.tex
Added complete analysis on thermal fragments, only left with fixing plots a bit

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	\widetilde{W}_{\rm{max}} &= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} \\
	&= \max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ (greater than $1$).
The threshold value of $1$ is achieved when the noise level $\epsilon$ is equal to
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise level threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
\begin{equation}
	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
For $\beta > \beta_{\rm{th}}$, $\epsilon_{\rm{th}}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = \beta_{\rm{th}}^{-1} \ln2.
\end{equation}

The maximum slope finally is
\begin{equation}
\widetilde{W}_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

Whenever the set of physical parameters falls under $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the first elbow coordinates can be read off the $X^0Y^0Z^0$ term in generating functions $G_n(\noisys), G_n(\gamma)$.
If it falls under $\rm{(C2)}$, then $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the first elbow coordinates can be read off the $X^0Y^nZ^0$ ($X^0Y^0Z^n$) term in generating functions $G_n(\noisys), G_n(\gamma)$,
\begin{equation}
	(x_0, L_0) =
	\begin{cases}
		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}

Considering the distillation process in~\cref{eq:msd_thermal}, the Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$.
In any case, a necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow and be expressed as
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

Let's focus on the case where both Lorenz curves are described by $\rm{(C1)}$.
This case includes the unital fragment.

The first elbow of the target state is located at $x'_0 = (3Z)^{-\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left( \frac{1}{3} - \frac{4}{9} \epsilon' \right)^{\tt}.
\end{equation}
The constraint in~\cref{eq:first_elbow_constraint} therefore holds only if
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon' \big)\Z_\beta  e^{\beta E_0} \Big]}}{\ln{\Big[ \big( 1-\frac{4}{3}\epsilon \big)\Z_\beta e^{\beta E_0} \Big]}} \\
	&= \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} - \beta (F_\beta - E_0)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} - \beta (F_\beta - E_0)},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. 
The free energy of thermal state $\gamma_\beta$ is denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}

Moreover, we can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon \leq \epsilon_{\rm{th}}$. \nick{In fact, it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level (lower than $\epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
At the limit of high temperature, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
    }
    \label{fig:distill_bounds_temp}
\end{figure}

Our approach also allows for analysis at the limit of low temperature, $\beta \rightarrow \infty$, which is a limit case of $\rm{(C2)}$ with $\beta \geq \beta_{\rm{th}}$.

We consider 
\begin{equation}
	x_\star = x_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{n}.
\end{equation}
The first elbow of the target state is located at $x'_0 = (e^{-\beta E_{\rm{max}}} / \Z_\beta)^{\tt} > x_\star$, so in order to find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$, we can interpolate between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_lowtemp}
	L'_\star = \frac{x_\star}{x'_0}L'_0 = \left(\frac{e^{-\beta E_2}}{\Z_\beta}\right)^{n-\tt} \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\tt}.
\end{equation}
Therefore, in the low temperature scenario $\beta \geq \beta_{\rm{th}}$, the constraint in~\cref{eq:first_elbow_constraint} holds only if
\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}}{\ln{\Big[ \big( \frac{1}{2}-\frac{1}{6}\epsilon \big)\Z_\beta e^{\beta E_{\rm{max}}} \Big]}} \nonumber\\
	&= \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)},
\end{align}
with $\tt \leq n$ and $\epsilon' \leq \epsilon$.

We can obtain an upper bound on thermal fragment distillation rate $R=n'/n$ for pure target Strange states ($\epsilon' = 0$) in this regime as well. 
It is given by
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
\end{equation}
which holds for all finite $n$ with $\tt \leq n$ and $\epsilon' \leq \epsilon$.
At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.
We compare $R(\beta)$ for different values of $\beta$ with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
    }
    \label{fig:distill_bounds_lowtemp}
\end{figure}

>>>>

Given an even value $\alpha$ for the sum, the term $\wn^{n-\alpha} \wp^{\alpha} e^{-\beta (n-\alpha)E_0}$ is fixed, so the expression is maximised by setting the coefficient of the highest energy $E_{\rm{max}}$ equal to $\alpha$.
Hence, we have
\begin{align}
	&\bmw(\noisys | \gamma)_{\rm{max}} = \nonumber\\
	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ (-\wn)^{n-\alpha} \wp^{\alpha} e^{\beta (n-\alpha)E_0} e^{\beta \alpha E_{\rm{max}}} \Big\}} = \nonumber\\
	&\max\limits_{\substack{\alpha = 0,2, \\ \dots,n-2,n}}{\Big\{ \wn^n e^{n\beta E_0} \left( \frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)} \right)^{\alpha} \Big\}}
\end{align}
The last expression is maximised for $\alpha = 0$ ($\alpha = n$) when the expression $\frac{u}{v} e^{\beta (E_{\rm{max}} - E_0)}$ is less than $1$ (greater than $1$).
The threshold value of $1$ is achieved when the noise level $\epsilon$ is equal to
\begin{equation}
	\epsilon_{\rm{th}} \coloneqq 3 - \dfrac{18}{8-e^{(E_{\rm{max}} - E_0)\beta}}.
	%\beta \leq \frac{1}{E_{\rm{max}} - E_0}\ln{\left( 8-\frac{18}{3-\epsilon} \right)}
\end{equation}
The noise level threshold $\epsilon_{\rm{th}}$ is a decreasing function of $\beta$.
It achieves its maximum value $3/7$ for $(E_{\rm{max}} - E_0)\beta = 0$, and a value equal to $0$ for
\begin{equation}
	\beta_{\rm{th}} \coloneqq \frac{1}{E_{\rm{max}} - E_0} \ln2.
\end{equation}
For $\beta > \beta_{\rm{th}}$, $\epsilon_{\rm{th}}$ is negative, meaning that the noise level $\epsilon$ will always be higher than the threshold.
We highlight that the threshold becomes $0$ when the difference between the maximum energy level and the level associated with the state negativity is equal to the energy extracted from a single particle Szilard's engine,
\begin{equation}
	E_{\rm{max}} - E_0 = \beta_{\rm{th}}^{-1} \ln2.
\end{equation}

The maximum slope finally is
\begin{equation}
\bmw(\noisys | \gamma)_{\rm{max}} =
	\begin{cases}
		\wn^n e^{n\beta E_0}, &\epsilon \leq \epsilon_{\rm{th}},\ \hspace{30pt}\rm{(C1)}	\\
		\wp^n e^{n\beta E_{\rm{max}}}, &\epsilon > \epsilon_{\rm{th}}.\ \hspace{32pt}\rm{(C2)} 
	\end{cases}
\end{equation}
Case 1 $\rm{(C1)}$ corresponds to the region labelled by $(i,j,k) = (0,0,0)$.
Case 2 $\rm{(C2)}$ corresponds to the region labelled by 
\begin{equation}
	(i,j,k) = 
	\begin{cases}
	(0,n,0), &\text{if } E_{\rm{max}} = E_1, \\
	(0,0,n), &\text{if } E_{\rm{max}} = E_2.
	\end{cases}
\end{equation}
Note that if $E_{\rm{max}} = E_0$, we get $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all $\epsilon$ and $\beta$.
Assuming $E_{\rm{max}} > E_0$, we get the cases:
\begin{itemize}
	\item $\beta = 0$. Then, $\epsilon_{\rm{th}} = 3/7$ and $\rm{(C1)}$ holds for all noise levels $\epsilon$.
	This is the unital fragment.
	\item $0 < \beta < \beta_{\rm{th}}$. Then, $0 < \epsilon_{\rm{th}} < 3/7$ and $\rm{(C1)}$ holds for $\epsilon \leq \epsilon_{\rm{th}}$, while $\rm{(C2)}$ holds for $\epsilon \geq \epsilon_{\rm{th}}$.
	\item $\beta \geq \beta_{\rm{th}}$. Then, $ \epsilon_{\rm{th}} \leq 0$ and $\rm{(C2)}$ holds for all $\epsilon$.
\end{itemize}

In $\rm{(C1)}$, the multiplicity is $m_{000} = 1$ and the corresponding Wigner components are $\bmw(\noisys)_{000}, \bmw(\gamma)_{000}$.
In $\rm{(C2)}$, we have $E_{\rm{max}} = E_1$ ($E_{\rm{max}} = E_2$), the multiplicity is $m_{0n0} = 3^n$ ($m_{00n} = 3^n$) and the corresponding Wigner components are $\bmw(\noisys)_{0n0}, \bmw(\gamma)_{0n0}$ ($\bmw(\noisys)_{00n}, \bmw(\gamma)_{00n}$).
The first elbow coordinate expression can finally be expressed as
\begin{equation}\label{eq:first_elb_coords}
	(x_0, L_0) =
	\begin{cases}
		\left( \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n, \wn^n \right), &\rm{(C1)}	\vspace{10pt}\\
		\left( \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n, (3u)^n \right). &\rm{(C2)} 
	\end{cases}
\end{equation}

Consider the distillation process in~\cref{eq:msd_thermal},
\begin{equation*}
		\noisys(\epsilon)\too{n} \xrightarrow{\E \in \O_{\gamma_\beta}} \noisys(\epsilon')\too{\tt} \otimes \gamma_\beta\too{(n-\tt)},
\end{equation*}
with $n > n'$ and $\epsilon > epsilon'$.
A necessary distillation constraint can be defined at the location $x_\star = x_0$ of the initial state's first elbow, expressed as
\begin{equation}\label{eq:first_elbow_constraint}
	\lc{\noisys(\epsilon)\too{n}}{\gamma_\beta}(x_\star) \geq \lc{\noisys(\epsilon')\too{\tt}}{\gamma_\beta}(x_\star).
\end{equation}

The Lorenz curves of the initial and target states may each be described by either $\rm{(C1)}$ or $\rm{(C2)}$, depending on the physical parameters $\epsilon, \epsilon', \beta$.
Specifically, we can get three scenarios:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.
\end{enumerate}
Note that $\rm{(C1)} \rightarrow \rm{(C2)}$ is impossible because it would imply $\epsilon \leq \epsilon_{\rm{th}} \leq \epsilon' < \epsilon$, a contradiction.

In all three scenarios, it is simple to check that the first elbow of the initial state is always located closer to $0$ compared to the first elbow of the target state, $x_0 \leq x_0'$:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$. 
	It is always true that $e^{-\beta E_0} / \Z_\beta \leq 1$, so
	\begin{align*}
		x_0 &= \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{n-\tt} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} = x_0'		
	\end{align*}
	\item $\rm{(C2)} \rightarrow \rm{(C1)}$.
	It is always true that
	\begin{align*}
		&\Z_\beta^{n-\tt} > (e^{-\beta E_{\rm{max}}})^{n-\tt} = e^{-\beta (n-\tt) E_{\rm{max}}}, \text{ so} \\
		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \dfrac{e^{-\beta(n E_{\rm{max}} - \tt E_0)}}{\Z_\beta^{n-\tt}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
		&< \dfrac{e^{-\beta(n E_{\rm{max}} - \tt E_0)}}{e^{-\beta (n-\tt) E_{\rm{max}}}} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
		&= e^{-\beta \tt (E_{\rm{max}} - E_0)} \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} \\
		&< \left(\dfrac{e^{-\beta E_0}}{3\Z_\beta}\right)^{\tt} = x_0'.
	\end{align*}
	\item $\rm{(C2)} \rightarrow \rm{(C2)}$.
	It is always true that $e^{-\beta E_{\rm{max}}} / \Z_\beta \leq 1$, so
	\begin{align*}
		x_0 &= \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^n = \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{n-\tt} \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{\tt} \\
		&\leq \left(\dfrac{e^{-\beta E_{\rm{max}}}}{\Z_\beta}\right)^{\tt} = x_0'	
	\end{align*}
\end{enumerate}
We can thus find the target state Lorenz curve coordinate $L'_\star$ at location $x_\star$ by interpolating between the origin and the target state's first elbow, 
\begin{equation}\label{eq:constraint_deriv_temp}
	L'_\star = \frac{x_\star}{x'_0}L'_0.
\end{equation}
We need $L_0 \geq L_\star'$. Therefore, restricting to the first elbow, the necessary distillation condition in~\cref{eq:first_elbow_constraint} simply becomes
\begin{equation}\label{eq:first_elb_bound}
	\frac{L_0}{x_0} \geq \frac{L_0'}{x_0'}.
\end{equation}
Involving more elbows gives stricter, but more convoluted necessary distillation constraints.

We now compute distillation bounds based on the first elbow constraint in the three possible scenarios.
We express them in terms of the free energy of thermal state $\gamma_\beta$ denoted by
\begin{equation}
	F_\beta \coloneqq \tr[\gamma_\beta H] + \beta^{-1} \tr[\gamma_\beta \ln{\gamma_\beta}] = -\beta^{-1} \ln{\Z_\beta}.
\end{equation}
Substituting coordinates from~\cref{eq:first_elb_coords} appropriately in~\cref{eq:first_elb_bound}, we get the following necessary conditions:
\begin{enumerate}
	\item $\rm{(C1)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} = E_0$ OR $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' < \epsilon  \leq \epsilon_{\rm{th}}$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( 1-\frac{4}{3}\epsilon \big)} + \beta (E_0 - F_\beta)}, \text{ or} \\
	\epsilon &\leq \frac{3}{4} - \frac{3}{4} \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \left( \frac{e^{-\beta E_0}}{\Z_\beta} \right)^{1 - \frac{\tt}{n}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left( \frac{1}{1 - \frac{4}{3}\epsilon} \right)}}{\beta (E_0 - F_\beta)},
\end{equation}

	\item $\rm{(C2)} \rightarrow \rm{(C1)}$ if $E_{\rm{max}} > E_0$, $\beta < \beta_{\rm{th}}$ and $\epsilon' \leq \epsilon_{\rm{th}} < \epsilon$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( 1-\frac{4}{3}\epsilon' \big)} + \beta (E_0 - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
	\epsilon &\leq 3 - 6 \left( 1 - \frac{4}{3}\epsilon' \right)^{\frac{\tt}{n}} \frac{e^{-\beta E_{\rm{max}}} e^{\frac{\tt}{n}\beta E_0}}{\Z_\beta^{1-\frac{\tt}{n}}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)} + (E_{\rm{max}} - E_0)(\beta_{\rm{th}} - \beta)}{\beta (E_0 - F_\beta)},
\end{equation}

	\item $\rm{(C2)} \rightarrow \rm{(C2)}$ if $E_{\rm{max}} > E_0$, $\beta \geq \beta_{\rm{th}}$.

\begin{align}
	\frac{n}{n'} &\geq \frac{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon' \big)} + \beta (E_{\rm{max}} - F_\beta)}{\ln{\big( \frac{1}{2}-\frac{1}{6}\epsilon \big)} + \beta (E_{\rm{max}} - F_\beta)}, \text{ or} \\
	\epsilon &\leq 3 - 6 \left( \frac{1}{2} - \frac{1}{6}\epsilon' \right)^{\frac{\tt}{n}} \left( \frac{e^{-\beta E_{\rm{max}}}}{\Z_\beta} \right)^{1 - \frac{\tt}{n}}	
\end{align}
This leads to an upper bound for the distillation rate $R=n'/n$ of pure Strange states ($\epsilon' = 0$),
\begin{equation}
	R \leq R(\beta) \coloneqq 1 - \frac{\ln{\left(\frac{1}{1-\frac{1}{3}\epsilon} \right)}}{-\ln{2} + \beta (E_{\rm{max}} - F_\beta)},
\end{equation}
\end{enumerate}

Consider pure Strange state distillation at high temperatures, $\beta \leq \beta_{\rm{th}}$.
Depending on the noise level of the initial state, we have either a $\rm{(C1)} \rightarrow \rm{(C1)}$ or a $\rm{(C2)} \rightarrow \rm{(C1)}$ scenario.

We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_temp}.
At every $\beta > 0$, the rates indicate a transition at $\epsilon_{\rm{th}}$.
As $\beta$ increases, the rate becomes stricter.
At the high temperature limit, $\beta \rightarrow 0$, we get $\beta F_\beta \rightarrow -\ln{3}$, and we retrieve the unital fragment bound,
\begin{equation}
	R(\beta) \xrightarrow{\beta \rightarrow 0} \frac{\ln{(3-4\epsilon)}}{\ln{3}}.
\end{equation}

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_temp.pdf}
    \caption{\textbf{Distillation rate with low noise in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ for low noise levels $\epsilon \leq \epsilon_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$ such that $0 \leq \beta \leq \beta_{\rm{th}}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    As $\beta$ increases, the range of noise levels for which $R(\beta)$ is valid decreases and the distillation bound becomes stricter.
\nick{it holds for $0 \leq \epsilon \leq \epsilon_*$, where $\epsilon_\star$ is the noise level ($ \leq \epsilon_{\rm{th}}$) at which the state conversion turns from $\rm{(C1)} \rightarrow \rm{(C1)}$ to $\rm{(C2)} \rightarrow \rm{(C1)}$. Need to adjust~\cref{fig:distill_bounds_temp} accordingly}
    }
    \label{fig:distill_bounds_temp}
\end{figure}

Consider pure Strange state distillation at low temperatures, $\beta \rightarrow \infty$.
Independently of the noise level of the initial state, we have a $\rm{(C2)} \rightarrow \rm{(C2)}$ scenario.

We compare $R(\beta)$ for different temperatures with the mana bound $R_{\rm{mana}}$ in~\cref{fig:distill_bounds_lowtemp}.
As $\beta$ decreases, the rate becomes stricter.
At the zero temperature limit, $F_\beta$ tends to zero, so $R(\beta) \xrightarrow{\beta \rightarrow \infty} 1$.

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.5]{figs/distill_bounds_lowtemp.pdf}
    \caption{\textbf{Distillation rate for low temperatures in thermal fragments.} Distillation rates obtained by majorization $R(\beta)$ in the temperature regime $\beta \geq \beta_{\rm{th}}$ are plotted for different temperatures $\beta^{-1}$.
    The mana distillation rate $R_{\rm{mana}}$ is given for comparison.
    The Hamiltonian spectrum is simple harmonic, $(E_0, E_1, E_2) = (0,1,2)$.
    \nick{Not-so-good bound for low temperatures, other elbows perform a lot better numerically.}
    }
    \label{fig:distill_bounds_lowtemp}
\end{figure}
